Geospatial - Assignment 3

### 2025-02-13 hw3/hw3_MoritzPeistNoemiLucchiSimonVellin.Rmd
Fixes

---
title: "Geospatial - Assignment 3"
author: 
- Moritz Peist
- Noemi Lucchi
- Simon Vellin
output:
  html_notebook:
    toc: true
  pdf_document:
    toc: true
---

@@

# Disable warning messages and SVG plots
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  # fig.ext = "svg",
  fig.width = 16,
  fig.height = 8,
  fig.retina = 2,
  dpi = 300,
  dev = "svg"
)
```

@@

@@

@@

![Figure 2](data/ex2/raster08.png)

>>>>

---
title: "Geospatial - Assignment 3"
author:
- Moritz Peist
- Noemi Lucchi
- Simon Vellin
output:
  html_document:
    toc: true
    df_print: paged
  pdf_document:
    toc: true
  html_notebook:
    toc: true
---

@@

# Disable warning messages and SVG plots
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  # fig.ext = "svg",
  fig.width = 16,
  fig.height = 8,
  fig.retina = 2,
  dpi = 300
  # dev = "svg"
)
```

@@

<div style="text-align: center">

@@

</div>

@@

<div style="text-align: center">

  ![Map 2](data/ex2/raster08.png)

</div>
